Discrete Ordinates

### 2017-06-09 docprep/chapimpl.tex
Updated the implementation chapter

This chapter covers the details of the implementation of the different components of the DOCTORS code base. The code is available from a GitHub Git repository. At the time of this writing, the repository is located at \texttt{https://github.com/eNorris/thesis} and is only available subject to special request and license agreement. An executable version is available.

@@

Data is stored in large, multi-dimensional arrays. For example, the CT voxel phantom can be intuitively stored as a 3D array of floating precision values which can be easily indexed. However, DOCTORS is written such that it is extensible to GPUs. GPUs are not optimized for data stored in a multi-dimensional fashion, but rather for data stored as a single 1-dimensional array. To emulate the 3-dimensional storage arrangement of the data, indexing arithmetic is used.

On the CPU, data is stored as C++ \texttt{std::vector<T>} objects where the \texttt{T} template parameter can be either \texttt{float} or \texttt{double} depending on the precision (32 bits or 64 bits respectively) needed. The storage space available to a \texttt{std::vector<T>} object is effectively unlimited, bounded only by the host CPU's physical RAM. However, other effects such as memory fragmentation can limit the practical size of a single, continuous \texttt{std::vector<T>} object significantly. To emulate indexing of a $N_x \times N_y$ matrix, a single \texttt{std::vector<T>} is created and resized to $N_x \times N_y$ elements. The global index, $i$, in the flattened array is then
\begin{equation}
i = i_x N_y + i_y.
\end{equation}
This pattern extends to multi-dimensional matrices. For example, a $N_x \times N_y$ matrix would be globally indexed as
\begin{equation}
i = i_x N_y N_z + i_y N_z + i_z.
\end{equation}

@@

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/indx_ex}
  \end{center}
  \caption{Conversion from 3D indexing to 1D "flattened" indexing.}
\label{fig:indx_ex}
\end{figure}

>>>>

This chapter covers the details of the implementation of the different components of the DOCTORS code base.

The code is available from a GitHub Git repository. At the time of this writing, the repository is located at \texttt{https://github.com/eNorris/thesis} and is only available subject to special request and license agreement. An executable version is available.

@@

Data is stored as \texttt{std::vector<>} objects.

@@

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/indx_ex}
  \end{center}
  \caption{The indexing scheme.}
\label{fig:indx_ex}
\end{figure}
